Extended Data

### 2022-02-21 doc/manuscript/Dow_Extended_Data.Rmd
Update Dow_Extended_Data.Rmd
#112

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring-porous","diffuse-porous","ring-porous", "diffuse-porous"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 2, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 9, 12, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Phenological temperature sensitivity* (days/°C)", 13, 22, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(14:17)%>%
    add_indent(19:22)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Phenological temperature sensitivity refers to the sensitivity of a parameter to the mean maximum temperature ($T_{max}$) during the critical temperature window (Fig. 1). Because leaf phenology measurements were derived from satellite imagery and included both ring- and diffuse-porous trees, the selection of a critical window was less straightforward. We used the critical window identified for diffuse-porous trees as the critical window for leaf phenology calculations because they included a wider range of spring dates.

>>>>

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring-porous","diffuse-porous","ring-porous", "diffuse-porous"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 2, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 9, 12, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Phenological temperature sensitivity* (days/°C)", 13, 22, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(14:17)%>%
    add_indent(19:22)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Phenological temperature sensitivity refers to the sensitivity of a parameter to the mean maximum temperature ($T_{max}$) during the critical temperature window (Fig. 1). Because leaf phenology measurements were derived from satellite imagery and included both ring- and diffuse-porous trees, the selection of a critical window was less straightforward. We used the critical window which had the greatest correlation with leaf greenup timing as the critical window for leaf phenology calculations.
